TRITON: Globally Consistent Sim-to-Real Transfer

### 2022-06-04 CORL/example.tex
Added figures

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
	\end{center}
	\caption{
		This is the main diagram for the paper. $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		TODO: Use variables instead of 3,4
		TODO: Make the text larger and easier to read
		TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/unprojection_consistency_loss.pdf}
	\end{center}
	\caption{
		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $\u_{1...R,1...L}$, 
	}
	\label{fig:unprojection_consistency_loss}
\end{figure}

>>>>

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
	\end{center}
	\caption{
		We use differentiable rendering paired with unpaired image translation to consistently transform synthetic scenes into realistic images.
		To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
		This texture is parametrized as an image generated by an MLP which is fed fourier features, as shown in figure 
		$B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		Inputs are on the left, and outputs are on the right.
		The dashed arrows indicate losses between nodes.
		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		% TODO: Use variables instead of 3,4
		% TODO: Make the text larger and easier to read
		% TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/unprojection_consistency_loss.pdf}
	\end{center}
	\caption{
		This is the unprojection consistency loss used in figure \ref{fig:main_diagram}.
		After calculating fake photos $\hat{p}_{1...B}$ from UVL scenes $s_{1...B}$ as seen in figure \ref{fig:main_diagram}, 
		we can unproject fake photos $\hat{p}_{1...B}$ back into texture space to obtain $u_{1...R,\ 1...L}$ .
		If the fake photos display consistent textures along their 3d surfaces, then the unprojected textures should be similar.
		We can measure this similarity by taking the per-channel standard deviation of these unprojections, aka $\sigma(u)$ , then averaging the result.
		When the fake photos display similar surfaces, the unprojections will be similar making the unprojection consistency loss low.
		Additionally, we can also calculate the average unprojection, which is useful for visualization purposes (it will look blurry if $\hat{p}$ is inconsistent).
	}
	\label{fig:unprojection_consistency_loss}
\end{figure}

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=400pt]{../images/learnable_textures.pdf}
	\end{center}
	\caption{
		Hello
	}
	\label{fig:unprojection_consistency_loss}
\end{figure}
